\documentclass[11pt,letterpaper,english]{article}

% Page design
\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry}
\pagestyle{empty}

% General packages
\usepackage[T1]{fontenc}
%\usepackage{txfonts}
\usepackage{xcolor}
%\usepackage{eqnarray}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{setspace}
\newcommand{\verbatimfont}[1]{\renewcommand{\verbatim@font}{\ttfamily#1}}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{multirow}
\usepackage{floatrow}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{hhline}
\setlength\doublerulesep{.7pt}
%\usepackage{tabularx}
\usepackage{subcaption}

%\usepackage{csmacros}
\usepackage{dsfont}
%\input{csvers.tex}

% Section format
\usepackage{sectsty}
\sectionfont{\normalsize}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}
\usepackage{titlesec}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}

\titlespacing\section{0pt}{0\parskip}{0\parskip}
\titlespacing\subsection{0pt}{0\parskip}{0\parskip}
\titlespacing\subsubsection{0pt}{0\parskip}{0\parskip}
\titleformat{\section}[block]{\normalfont\normalsize\bfseries}{\thesection .}{1em}{}
\titleformat{\subsection}[block]{\normalfont\normalsize\bfseries}{\thesubsection .}{1em}{}
\titleformat{\subsubsection}[block]{\normalfont\normalsize\bfseries}{\thesubsubsection .}{1em}{}

% Bibliography format

\usepackage[hidelinks]{hyperref}
\usepackage[numbers]{natbib}
\usepackage{doi}
\renewcommand{\refname}{REFERENCES}
\makeatletter
\renewcommand\@biblabel[1]{#1.\em}
\makeatother
\setlength{\bibsep}{0pt plus 0.3ex}

% Captions
\usepackage{caption}
\captionsetup[figure]{labelfont={bf,normalsize},textfont={bf,normalsize},labelformat={default},labelsep=period,name={Figure}}

% Tables
\floatsetup[table]{capposition=top}
\captionsetup[table]{labelfont={bf,normalsize},textfont={bf,normalsize},labelformat={default},labelsep=period,name={Table}}
\renewcommand{\thetable}{\Roman{table}}
\captionsetup[sub]{font={normalsize},labelfont={bf,normalsize}}

% UDF
\definecolor{brown}{RGB}{74,68,42}
\newcommand{\tw}[1]{#1\textwidth}
\newcommand{\lw}{\linewidth}
\renewcommand{\eqref}[1]{(\ref{#1})}

\raggedright

\begin{document}
\vspace*{-0.45in}
\begin{center}
{\Large\centering\bf CARDINAL: A MULTIPHYSICS SIMULATOR FOR PEBBLE BED REACTORS}

\vspace{3pt}

{\bf \large Elia Merzari} \\
\large Pennsylvania State University \\
\large 228 Hallowell, University Park, PA, USA \\
{\color{brown} ebm5351@psu.edu} \\

\vspace{0.25in}

{\bf \large Haomin Yuan, Paul Fischer, Misun Min, Dillon Shaver,} \\
{\bf \large Ronald Rahaman, Patrick Shriwise, Paul Romano } \\
{\bf \large Alberto Talamo, Yu-Hsinag Lan } \\
\large Argonne National Laboratory \\
\\
\vspace{0.45in}
\\
{\bf \large Derek Gaston, Richard Martineau} \\
\large Idaho National Laboratory \\
 \\
\vspace{0.45in}
 \\
{\bf \large  Yassin Hassan } \\
\large Texas A&M University \\


\end{center}



\normalsize

\section*{ABSTRACT}


In this article we demonstrate a multi-physics solver for pebble bed reactors and in particular for  the Berkley's PB-FHR (Fluoride Cooled High Temperature Reactors) Mark-I design. The
Fluoride salt cooled High temperature Reactor (FHR) is a class of advanced nuclear reactors that combine the
robust coated particle fuel form from high temperature gas cooled reactors, direct reactor auxiliary cooling
system (DRACS) passive decay removal of liquid metal fast reactors, and the transparent, high volumetric heat capacitance liquid Fluoride salt working fluids - Flibe - from molten salt reactors. This combination of fuel and coolant enables FHRs to operate in a high-temperature low-pressure design space that has beneficial safety and economic implications. The PB-FHR reactor relies on a pebble bed approach and pebble bed reactors are in a sense the poster child for multiscale analysis.

Relying heavily on MOOSE's MultiApp capability we have developed Cardinal, a new tool platform for lower length-scale simulation for pebble bed cores. The lower length-scale simulator comprises three physics: neutronics (OpenMC), thermal-fluids (Nek5000/NekRS) and fuel performance (BISON).   Cardinal tightly couples all three physics and leverages advances in MOOSE such as the MultiApp system and the concept of MOOSE-wrapped Apps. Moreover Cardinal can run part of the physics on  GPUs. In this manuscript we discuss the development of Cardinal, verification and validation and demonstration simulations.

\begin{flushright}
{\bf KEYWORDS} \\
Pebble Bed, FHR, Multi-physics
\end{flushright}

\doublespacing

\input intro
\input cardinal
\input vv
\input demo
\input concl


%\bibliographystyle{ieeetr}
\bibliographystyle{nureth18new}
%\bibliographystyle{ans}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
\bibliography{references}
%\bibliographystyle{abbrv}

\begin{center}
\scriptsize
\framebox{\parbox{2.6in}{The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory
("Argonne").  Argonne, a U.S. Department of Energy Office of Science laboratory, is operated under Contract No. DE-AC02-06CH11357.  The U.S. Government retains for itself, and others acting on its behalf, a paid-up, nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.}}
\normalsize
\end{center}


\end{document}
